Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-07-31 Papers/ViscousInstabilities/article_figure1.tex
updates: adding figures for the qualitative validation -- Section 4.2 ... text to come ...

%%%%
%%%%  FIGURE 
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{-0.3cm}
%\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_2.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{3.5cm} (a) Schematics of the domain with permeability ($\mathbf{K}$) distribution
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{4.5cm} (b) flow at t=25
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (c) flow at t=3000   
}}     
\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=2.5$ and $\mathbf{K}_{2}=1$; (b-c) snapshots of saturation (displacing fluid) field at t=$25$ and t=$300$. The domain is discretised with $5960$ \PN[1]{2} elements. }
\label{fem_cv_represent_a}
\end{figure}
\clearpage

>>>>

%%%%
%%%%  FIGURE 
%%%%
%\begin{figure}[ht] 
%\vbox{
%\hbox{\hspace{-0.3cm}
%\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
%\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_2.pdf} 
%}
%\vspace{0.0cm}
%\hbox{\hspace{3.5cm} (a) Schematics of the domain with permeability ($\mathbf{K}$) distribution
%}
%\vspace{0.25cm}
%\hbox{\hspace{1.5cm}
%\includegraphics[width=.85\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
%}
%\vspace{0.0cm}
%\hbox{\hspace{4.5cm} (b) flow at t=25
%}
%\vspace{0.25cm}
%\hbox{\hspace{1.5cm}
%\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_2.pdf}
%}
%\vspace{0.0cm}
%\hbox{\hspace{4.0cm} (c) flow at t=3000   
%}}     
%\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=2.5$ and $\mathbf{K}_{2}=1$; (b-c) snapshots of saturation (displacing fluid) field at t=$25$ and t=$300$. The domain is discretised with $5960$ \PN[1]{2} elements. }
%\label{DaweGrattoniExperiment_a}
%\end{figure}
%\clearpage
%\end{comments}

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
    \vbox{
       \hbox{\hspace{1.cm}\includegraphics[width=\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_2}}
       \vspace{0.cm}
       \hbox{\hspace{7cm}(a)}
       \vspace{0.cm}
       \hbox{\hspace{1.cm}\includegraphics[width=\textwidth]{./Pics1/DaweGrattoni_Experiment/1pageb}}
       \vspace{0.cm}
       \hbox{\hspace{7cm}(b)}
    }   
\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) sketch of the the domain which is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=2.5$ and $\mathbf{K}_{2}=1$; (b) fluid displacement with permeability ratio of 2.5, exttracted from \citet{dawe_2008}. }
\label{DaweGrattoniExperiment_a}
\end{figure}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
  \begin{figure}[ht] 
    \vbox{\vspace{0.cm}
       \hbox{\hspace{1cm}\includegraphics[width=.50\textwidth]{./Pics1/DaweGrattoni_Experiment/CrossFlow_d61b}  \includegraphics[width=.50\textwidth]{./Pics1/DaweGrattoni_Experiment/CrossFlow_d125b}  \includegraphics[width=.50\textwidth]{./Pics1/DaweGrattoni_Experiment/CrossFlow_d145b} }
       \hbox{\hspace{1cm}\includegraphics[width=.50\textwidth]{./Pics1/DaweGrattoni_Experiment/CrossFlow_d152b}  \includegraphics[width=.50\textwidth]{./Pics1/DaweGrattoni_Experiment/CrossFlow_d180b}  \includegraphics[width=.50\textwidth]{./Pics1/DaweGrattoni_Experiment/CrossFlow_d250b} }
       \hbox{\hspace{1cm}\includegraphics[width=.50\textwidth]{./Pics1/DaweGrattoni_Experiment/CrossFlow_d260b}  \includegraphics[width=.50\textwidth]{./Pics1/DaweGrattoni_Experiment/CrossFlow_d275b} \includegraphics[width=.50\textwidth]{./Pics1/DaweGrattoni_Experiment/legendb} }
       \vspace{0.cm}
    }  
\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): Snapshots of wetting fluid saturation overlapped with Darcy velocity over t=39.70 time-units. The domain is divided in four subdomains with permeabilities of $\mathbf{K}_{1}=2.5$ and $\mathbf{K}_{2}=1$. The domain is discretised with 37872 \PN[1]{2} triangular elements. }
\label{DaweGrattoniExperiment_b}
  \end{figure}
\end{landscape}
\clearpage
